Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2020-09-19 ehp_revision/response_to_reviewers.Rmd

\medskip

\begin{shaded}
\textbf{R1 Comment 2:}
Are there opportunities to expand this approach internationally? Some decisions
(e.g., county-level) data may restrict cross-country comparisons. Can the
authors discuss this? 
\end{shaded}

**Response:**

While there would be some limitations in comparisons based on differences in the
scale of county-equivalents, many countries affected by tropical cyclones do
have geopolitical areas that are fairly comparable to US counties, like
municipalities in Mexico and districts in India. There would be a few challenges,
however, in extending the exposure dataset for the hazards that we present in
this paper. We have added text to the paper's Discussion on opportunities and
barriers to expanding this approach internationally:

@@

**Response:**

Thank you for this suggestion. We have changed the wording in this sentence:

> **Text in revised manuscript (relevant change in bold):**
"In many cases, these studies analyze multi-year, multi-community data, allowing
them to estimate average associations over many disasters and to explore how a
disaster's characteristics, or the characteristics of the **affected
communities**, modify associated health risks (e.g., Anderson and Bell 2010; Son
et al. 2012; Liu et al. 2017)."

We also used the word "Hits per county per decade" in the legend for Figure 5 in
the main text (reproduced at the end of this response document as Figure
\@ref(fig:fig5)) and Figure S3 of the Supplemental Material. We have revised the
wording in these figures to "Exposures per county per decade".

@@

If, at the county level, there were strong agreement among exposure patterns for
the different tropical cyclone hazards we considered, it might have been
reasonable to recommend the use of a single hazard-based metric as a proxy for
exposure to all storm hazards in epidemiological studies for practical reasons.
We found that this is almost never the case, although there are a few select
storms (like Hurricane Floyd in 1999) where such an approach might be
justifiable. Most atmospheric scientists would not be surprised by our findings
about this disagreement in exposure patterns for different tropical cyclone
hazards, but this finding is not as self-evident for environmental
epidemiologists. Based on a recent conference of the International Society for
Environmental Epidemiology, for example, there are a number of environmental
epidemiologists with backgrounds focused on methods and other ambient exposures
(e.g., air pollution, heat) who are beginning to include tropical cyclones as an
exposure of interest in their studies, and we believe these results would be
novel and useful to many of them.

Further, in cases where it is clear that a mixture approach is necessary, these
results can help in understanding what challenges might arise in statistical
analysis. While one approach to including several hazards could be to create an
index of tropical cyclone exposure by taking a weighted sum of all hazards, for
most health outcomes it is unclear *a priori* what the weight for each hazard
should be in such an index, and so it will often be preferable to discover those
weights from the data by fitting a statistical model that includes each hazard
as an independent variable. In these cases, strong correlation (or agreement, in
the case of binary exposures) among separate independent variables can create
both numerical issues (e.g., variance inflation from multicollinearity) and
difficulties in interpretation (e.g., difficulty inferring the role of specific
hazards and separating the influence of each). If an epidemiologist has a good
understanding of these patterns in the data, he or she can adopt methods that
address potential issues, including using matching-based study designs to create
a subset of storms in which separate hazards are well-distinguished,
incorporation of dimension-reduction methods like principal
components analysis, or shrinkage techniques that allow for a small amount of
bias in estimation in return for reducing problems from
collinearity (e.g., ridge regression) [@leal2012multicollinearity;
@schisterman2017collinearity].

@@

The reviewer makes a good point that it is important for us to clarify our
motivation for measuring agreement between the hazard-based metrics, as well as
to show readers how our results from these measures can be used to help in
designing studies and planning statistical analysis for tropical cyclone
epidemiology. We have added text to the manuscript on these points:

> **Text in revised manuscript (relevant added text in bold):** 
"Finally, we investigated how well exposure assessment agreed across these
metrics. **These results can help epidemiologists answer several key
questions as they interpret previous research and design new studies. For
example, if a single storm hazard has been used to measure exposure in an
epidemiological study, can the result be interpreted as an association with
tropical cyclone exposure in general, or should it be limited to represent an
association with that specific storm hazard? If a study investigates the
association between a single storm hazard and a health outcome, could this
estimate be confounded by other storm hazards? When planning a new study that
will incorporate several storm hazards, might there be variance inflation from
multicollinearity or difficulties in disentangling the roles of separate
hazards?**"

@@

\textit{Line 514--515 from original manuscript:}

\begin{quotation}
\noindent
\textit{"The rainfall data are generally well-correlated with ground-based
observations, but may sometimes underestimate very high rainfall values (Figure
2)."}
\end{quotation}
\end{shaded}

**Response:**

This is a great suggestion. In the original manuscript, we describe this lower
correlation at higher precipitation values through the use of examples from
specific storms, and discuss the potential reasons for it. Measuring the
correlation specifically within these higher-precipitation events would add more
quantitative evidence to this discussion. We have added estimates of these
correlations specifically for high-precipitation events in a new table in the
Supplemental Material (Table S2 of the manuscript, reproduced as Table
\@ref(tab:highprecipcorr) at the end of this response document).

@@

\medskip

\begin{shaded}
\textbf{R2 Comment 3:}
Figure 4: I would add Y-axis label "NOAA classification."
\end{shaded}

**Response:**

This is a great suggestion. We have made this change, as well as several changes
in response to EHP's Request 4 later in this response. The original and revised
versions of Figure 4 of the manuscript are reproduced in Figure \@ref(fig:fig4)
at the end of this response.

@@

\textit{Line 600--602 from original manuscript:}

\begin{quotation}
\noindent
\textit{"Based on our results, the use of a distance-based metric to assess
exposure to any of these hazards, or the use of measurements from one hazard as
a proxy for exposure to any of the other hazards considered, would often
introduce exposure misclassification."}
\end{quotation}
\end{shaded}

**Response:**

Figure 7 of the main text is meant to help illustrate the potential for exposure
misclassification, including when using a distance-based metric as a proxy. We
used the Jaccard index because we are using data for all eastern US counties.
For any storm, there will be large parts of this area that are
unquestionably unaffected, because they are so far from the storm. For example,
during Hurricane Floyd in 1999, the storm made landfall in North Carolina and
moved northward along the Eastern Seaboard. While there will be questions in
some cases about whether counties in the Mid-Atlantic and New England were
exposed to this storm, counties in Texas, Louisiana, and other states in the
west of the study area were unquestionably unexposed to this storm. If we
measured misclassification using a metric that includes these counties in the
denominator, it would be overly optimistic because of the strong agreement in
counties far from the storm, like Texas counties during Hurricane Floyd, and
wouldn't help to pinpoint the potential for disagreement in areas nearer the
storm path.

@@

We have added text to introduce this supplemental table in the revised manuscript, 
both in the Methods and in the Discussion:

> **Text in the revised Methods (added text in bold)**:
"For other exposure metrics, each county was
classified as exposed to a tropical cyclone based on whether the exposure
metric exceeded a certain threshold (Table 1). We
picked reasonable thresholds (e.g., the threshold for gale-force wind for wind
exposure; **Table S1**), but others could be used with the open-source data and its
associated software."

> **Text in the revised Discussion (added text in bold)**:
"Finally, to assess patterns and agreement for binary exposure classifications,
we have chosen one set of sensible thresholds for binary classifications based
on continuous metrics (rainfall, maximum sustained surface wind, and distance
from the storm's track), **but other thresholds would be reasonable
depending on hypothesized pathways for a given epidemiological study (Table
S1)**."

\begin{longtable}{lp{35em}}
\caption{Reasons behind the choices of thresholds for binary exposure classifications, as well as discussion of some other reasonable choices. These are provided for the three exposure metrics for which our database includes continuous data, and so a threshold is selected to determine binary exposure based on the metric. This table provides reasoning for the choice of threshold used in this paper as well as guidance on other thresholds that could be considered, depending on the hypothesized pathways for an epidemiological study.} \\
\label{tab:thresholds} \\
\hline
Metric & Threshold choice\\
\hline
\textbf{Distance} & Distance-based exposure was determined based on whether the storm track came within 100 km of county population mean center. This threshold has been used in prior research as a proxy for exposure to hazards from the storm (e.g., Grabich et al. 2015a). Tropical cyclones vary dramatically in size: US tropical cyclones have been observed with radii to maximum winds as small as 20 km and as large as 200 km (Mallin and Corbett 2006; Quiring et al. 2011), and dangerous winds can extend beyond these maximum winds. One study assessed county-level risk and exposure based on a three-tiered definition, with primary counties being those closest to the storm track on either side, secondary counties being adjacent to primary counties, and tertiary counties adjacent to secondary counties, which resulted in an average distance radius of 120 km on either side of the storm track (Czajkowski et al. 2011). Other distance thresholds that could be considered include 60 km and 30 km, both of which have been used in previous research (Grabich et al. 2015a; Grabich et al. 2015b; Currie and Rossin-Slater 2013). However, based on the results presented in the main manuscript, hazard-based metrics should often be used directly rather than a distance-based proxy.\\

\textbf{Rain} & Rain-based exposure was determined based on whether the county had cumulative rainfall of $\ge75$ mm over the period from two days before to one day after the storm’s closest approach and the storm track came within 500 km of the county population mean center. One recent study has highlighted that a two-year rainfall value (which is the median annual maximum rainfall) for a location can provide a useful threshold in identifying rainfall events with potential for societal impacts (Bosma et al. 2020). For some of the more northern, inland communities included in our study area, the two-year rainfall value for two-, three- and four-day windows is in the 65--85 mm range. For example, Pittsburgh, PA, has two-year rainfall values of 69 mm for a two-day window, 74 mm for a three-day window, and 78 mm for a four-day window (US NOAA 2020), consistent with the 75 mm threshold we selected for exposure classification in this paper. However, other thresholds, particularly higher thresholds, would be reasonable in some cases. For example, the two-year rainfall values tend to be much higher in counties of the study area that are further south and close to the coast. The two-year rainfall value for Miami for a three-day window, for example is 180 mm (US NOAA 2020). A variety of definitions have been used previously to identify both extreme or heavy rain (whether associated with a tropical cyclone or not) and tropical cyclone--associated rain. In defining precipitation associated with tropical cyclones, studies have used thresholds of 12.5 mm per day as a metric of regions of ``moderately heavy'' rainfall (Zhou and Matyas 2017) and, as a lower threshold, a lower limit of 10 mm of total storm precipitation---\parfillskip=0pt\tabularnewline

&in conjunction with proximity to the storm's center---in identifying tropical cyclone precipitation events at a location (Feldmann et al. 2019). Other definitions of extreme rain events---including but not limited to tropical cyclone--associated rainfall---are higher than the threshold we use here---for example, one paper defined extreme rain events as cases in which a gauge reported 125 mm or more of rain in 24 hours (Schumacher and Johnson 2006). Studies have also used definitions that are relative to the norms for a given location (e.g., 24 hour rainfall totals over the 50-year return value for the location, which the part of the US east of the Rocky Mountains range from 3.5 in [89 mm] to 13 in [330 mm]) (Schumacher and Johnson 2006; Schumacher and Johnson 2005; Stevenson and Schumacher 2014).\\

\textbf{Wind} & Wind-based exposure was determined based on whether modeled storm-associated peak sustained surface wind was $\ge34$ kts at the county’s population mean center. This threshold is being applied to local winds for each county, and it represents the threshold for gale-force winds on the Beaufort wind scale. This limit is used as the outer limit in measuring storm size through the US National Hurricane Center's wind radii for tropical cyclone forecasts (Cangialosi and Landsea 2016). Other thresholds could be selected based on other points on the Beaufort scale---for example, $\ge48$ kts for capturing storm-force winds or $\ge64$ kts for capturing hurricane-force winds. As a note, hurricane-force winds will be rarely experienced for counties, as it will likely only be observed for very severe storms and even for those, only for counties near the storm's landfall. Many presentations of the Beaufort wind scale include descriptions of the conditions that winds in each category would produce both over land and at sea.\\
\hline
\end{longtable}

@@

\medskip

\begin{shaded}
\textbf{R3 Comment 7:}
Figure 3: The x-axis refers to one of the two wind data sources as "Extended
Best Tracks." Is this the same thing as the wind radii dataset described in the
text? Is so, I suggest clarifying this in the figure label.
\end{shaded}

**Response:**

Yes, it is the same. We have revised the x-axis on the figure to clarify that
the comparison is based on the wind radii dataset described in the text, as
requested. The original and revised versions of Figure 3 of the manuscript are
reproduced at the end of this response document as Figure \@ref(fig:fig3).

@@

# Requests from EHP: {-#requests-from-ehp}

\begin{shaded}
\textbf{EHP Request 1:}
Figure 3: Please truncate x-axis scale as you do for Figure S7. Since smallest
value is $\sim75\%$, this would make the data in the relevant range much easier to
appreciate.
\end{shaded}

**Response:**

We have revised this figure to show an x-axis truncated at the minimum observed
value ($\sim75\%$), as requested. The original and revised versions of this
paper are reproduced at the end of this response document as Figure \@ref(fig:fig3).

@@

\begin{shaded}
\textbf{EHP Request 2:}
Main text figures (general)
To ensure that figures are accessible to readers with impaired color vision, do not use color as the sole means of conveying information in a figure unless absolutely necessary. Use different symbols, shading/textures, and line patterns instead of (or in addition to) color to distinguish among different data points. Use contrasting colors that can be easily distinguished from each other when the figure is printed in black and white. For details, see: \url{https://ehp.niehs.nih.gov/authors/figures}.
\end{shaded}

**Response:**

In all these figures, we have used colormaps that are both accessible to readers
with several forms of color vision deficiency, including the most common type
(deuteranomaly, a type of red-green color vision deficiency), and can be easily
distinguished when the figure is printed in black and white [@viridis;
@van2015mpl]. The colormaps we used are all multi-hue sequential maps that avoid
red-green contrasts, while maximizing dynamic range in comparison to something
single-hued, like grayscale [@nunez2018optimizing; @viridis]. They are all
perceptually uniform across the scale for those with normal color vision
[@liu2018somewhere] and are close to perceptually uniform for those with common
forms of color deficiency [@nunez2018optimizing]. They reproduce their original
sequential gradient when printed in grayscale and so are perceptible when
printed on a black-and-white printer [@van2015mpl; @nunez2018optimizing].
Previous research has found that colormaps in this family allow viewers to more
quickly and accurately judge relative distances in scientific figures
[@liu2018somewhere]. The family of colormaps we used in the figures is currently
considered the gold standard for scientific figures [@nunez2018optimizing].

To help illustrate, in Figures \@ref(fig:fig5check1) and \@ref(fig:fig5check2)
at the end of this response document, we have reproduced the current version of
Figure 5 as it would appear to someone with three common types of color vision
deficiencies: deuteranomaly (defective green cone cells, the most common type),
as well as protanopia (defective red cone cells) and tritanopia (defective blue
cone cells). We have also shown how the Figure would appear in grayscale in
Figure \@ref(fig:fig5check2) (right). We have included similar versions of other
figures from the manuscript in response to later requests from EHP in this
response.

@@

\medskip

\begin{shaded}
\textbf{EHP Request 3:}
Figure 3: Please check the contrast between the colors used to indicate numbers
of counties. If you can see the gradient when printed in black and white it
should be ok, but some of the differences are very subtle. Truncating the x-axis
might help with this (if possible.)
\end{shaded}

**Response:**

As we note in our response to EHP Request 2, we used colormaps for all figures
that are designed to be perceptible both for those with common types of color
vision deficiency and when printed in grayscale. We have increased the size of
the circles in Figure 3 of the revised manuscript (reproduced in Figure
\@ref(fig:fig3) at the end of this response) so that the colors are clearer, as
well as truncated the x-axis as requested in EHP Request 1. Also, we show in
Figures \@ref(fig:fig3check1) and \@ref(fig:fig3check2) of this response how the
revised Figure 3 would look with three common types of color vision deficiency
as well as when printed in black and white. The gradient is clear when this
figure is printed in black and white.

@@

For the original figure, most of the events resulted in 0% of flood gages
exceeding the flood threshold, especially for events that were not recorded as
floods based on NOAA Storm Events. Therefore, most of the points in the original
were indeed dark blue, representing 0%, but we can see that readers might have
questioned if this was the case or if the scale made it harder to see subtler
differences.

We have made several changes to make this figure easier for readers to see and
interpret. These changes include:

- Binning the values shown by the points fill, so that readers only need to 
be able to distinguish among four colors, rather than across a larger scale.
- Increasing the size of the points, so the fill in each point is easier to 
see. 
- Using a different algorithm to "jitter" the points, so there are no points that
overlap each other.

We have reproduced both the original and revised versions of Figure 4 in the
manuscript as Figure \@ref(fig:fig4) at the end of this response.

@@

\medskip

\begin{shaded}
\textbf{EHP Request 5:}
Figures 5--6: Please check to see if the colors used can be distinguished if
printed in black and white, and if not, use a “color-blind friendly” palette if
possible. If this is not feasible, we can request an exemption from
accessibility requirements, but we try to do this only when alternatives  would
degrade the information content of  the figure.
\end{shaded}

@@

**Response:**

As we note in our response to EHP Request 2, we used colormaps for all figures
that are designed to be perceptible both for those with common types of color
vision deficiency and when printed in grayscale Figures \@ref(fig:fig5check1)
and \@ref(fig:fig5check2) at the end of this response show what Figure 5 of the
manuscript would look like under three common types of color vision deficiency
and when printed in black and white. Figures \@ref(fig:fig6check1) and
\@ref(fig:fig6check2) at the end of this response show the same thing for Figure
6 of the manuscript.

For Figure 6 of the manuscript, for some types of color vision deficiency, it
could be unclear which of the two color legends pairs with which part of the
graph. We have therefore added a note to the figure legend to clarify:

### 2020-09-19 ehp_revision/response_to_reviewers.Rmd

# Overview {-#overview}

\colorlet{shadecolor}{blue!8}
\begin{shaded}
\textbf{Associate Editor's Overview:}
Developing a consistent and comparable metric for exposure to tropical cyclones
would be a valuable addition to the literature. All reviewers had questions
about the exposure metric, including the challenges of using county-level data
where not everyone in a county would have been exposed and the difficulties of
going from country-level to individual-level risks. Further the comparison of
different storm hazards could be clarified. The reviewers identified several
issues where further explanation would increase the accessibility of the
manuscript.
\end{shaded}

Thank you for the opportunity to revise and resubmit this manuscript. We
appreciate the helpful suggestions from the reviewers for clarifying and
deepening the discussion in the paper.

The larger changes we have made include:

1. Added discussion on the challenges and limitations of using aggregated, 
county-level exposure assessment.
2. Added explanations for how our comparisons among different storm hazards
can help epidemiologists in designing studies and planning statistical analysis.
3. Added a supplemental table explaining the choice of thresholds for binary 
exposure classification.
3. Added a small analysis of the correlation in rainfall metrics specifically
in cases of high rainfall ($\ge75$ mm of cumulative rainfall in the county
associated with the storm), to deepen the discussion of potential disagreement
in continuous measures of rainfall during extreme conditions. 
4. Added supplemental tables that provide more details on patterns of exposure
misclassification when comparing each hazard-based metric to a distance-based
proxy metric.
4. Changed labeling, axis range, and other presentation details for some
figures, as well as confirmed that the color scales will be accessible.
5. Corrected typos and improved wording throughout based on suggestions of the
reviewers.

@@

\medskip

\begin{shaded}
\textbf{Reviewer 1 (R1) Comment 1:}
I very much appreciate the rationale for authors' decision to focus at the
county level, especially given the available health-related data. But, since
tropical cyclones don't necessarily have consistent impacts across an entire
county, I think the limitations of this decision are worthy of further
discussion in the discussion section.
\end{shaded}

**Response:**

\hl{Roger and Meilin, could you take a look at this response and let me know if
you have any comments of suggestions to add?}

@@

\medskip

\begin{shaded}
\textbf{R1 Comment 2:}
Are there opportunities to expand this approach internationally? Some decisions
(e.g., county-level) data may restrict cross-country comparisons. Can the
authors discuss this? 
\end{shaded}

**Response:**

\hl{Andrea, Mohammad, Seth, Steven, Bill, could you take a look at this response 
and let me know if you have any comments of suggestions to add?}

@@

\medskip

\begin{shaded}
\textbf{R1 Comment 6:}
This is not a comment on the paper, but the authors may also want to consider
publishing their work in DesignSafe, which is "the web-based research platform
of the NHERI  [NSF-Funded Natural Hazards Engineering Research Infrastructure]
Network that provides the computational tools needed to manage, analyze, and
understand critical data for natural hazards research." It is the data
repository widely used by interdisciplinary hazards and disaster researchers.
\end{shaded}

**Response:**

\hl{Dirk, could you take a look at this response and let me know if you have
any comments of suggestions to add? In particular, I don't have a lot of experience
working with cloud-based platforms with Jupyter Notebooks. It sounds like that's 
how the workspace for this DesignSafe platform works. My best guess is that you'd
be able to download and use R packages in that type of workspace, including 
a package hosted on a drat repository. Do you have any experience or insights on
installing packages from different repositories while working on a Jupyter Notebook
through an online platform?}

@@

\medskip

\begin{shaded}
\textbf{Reviewer 3 (R3) Comment 1:}
Starting on line 128, the authors write "Extreme winds are more common to the
track's right, where counterclockwise cyclonic winds move in concert with the
tropical cyclone's forward motion". I think this statement may be specific to
tropical cyclones in the Northern hemisphere (i.e., those relevant to exposure
in the US). Would be good to clarify this.
\end{shaded}

**Response:**

\hl{Andrea, could you take a look at this response and let me know if you have
any comments of suggestions to add?}

@@

\medskip

\begin{shaded}
\textbf{R3 Comment 6:}
Table 1: I suggest providing the rationale for picking the thresholds for
classifying continuous exposures into binary ones within the table. 
\end{shaded}

**Response:**

\hl{Andrea, Mohammad, Seth, Steven, and Bill, could you take a look at this
response and let me know if you have any comments of suggestions to add?}

### 2020-09-22 ehp_revision/response_to_reviewers.Rmd

\begin{shaded}
\textbf{Reviewer 1 (R1) Comment 1:}
I very much appreciate the rationale for authors' decision to focus at the
county level, especially given the available health-related data. But, since
tropical cyclones don't necessarily have consistent impacts across an entire
county, I think the limitations of this decision are worthy of further
discussion in the discussion section.
\end{shaded}

**Response:**

This is an excellent point. We have added text in the Limitations section of the
Discussion on the potential limitations of using aggregated, county-level
exposure data in a research study:

> **Text added to Discussion (added text in bold):** 
"Second, these data are aggregated to the county level. **This spatial scale
allows for easy integration with health outcome data aggregated at the county
level, and disaster response decisions are often made at a county or state
level. Such data is often used for disaster epidemiology, as aggregated data may
be easier to access than individual-level data, especially at a scale that
covers many locations and years and so allows higher statistical power and
includes a broader range of exposure levels [@wakefield2008overcoming].**

@@

\begin{shaded}
\textbf{R1 Comment 2:}
Are there opportunities to expand this approach internationally? Some decisions
(e.g., county-level) data may restrict cross-country comparisons. Can the
authors discuss this? 
\end{shaded}

**Response:**

While there would be some limitations in comparisons based on differences in the
scale of county-equivalents, many countries affected by tropical cyclones do
have geopolitical areas that are fairly comparable to US counties, like
municipalities in Mexico and districts in India. There would be a few challenges,
however, in extending the exposure dataset for the hazards that we present in
this paper. We have added text to the paper's Discussion on opportunities and
barriers to expanding this approach internationally:

> Text added to the Discussion (added text in bold): 
"**This dataset is limited to the contiguous US, and while expansion to global
coverage would be useful and feasible, there would be some challenges. The key
challenge would be for tornado and flood events. For these events, the data
described in this paper drew on a US-focused storm events database, and so
international extension of data on these hazards would require access to similar
databases covering other countries. For precipitation data, while the
re-analysis product used here (NLDAS-2) only covers the contiguous US, other
re-analysis products, as well as other types of precipitation datasets, have
global coverage [@sun2018review], including the NASA Global Land Data
Assimilation System Version 2 (GLDAS-2; @rodell2004global), the Global
Precipitation Measurement Mission (GPM), and the Tropical Rainfall Measuring
Mission (TRMM). The wind data are generated based on a model that is currently
US-focused [@stormwindmodel], but could be extended to other areas, although
this would require adding new land/sea masks within the associated software, as
well as accounting for differences across storm basins in wind averaging periods
[@harper2010guidelines]. Further, since the core of the wind model was developed
based on data from Atlantic-basin storms [@willoughby2006parametric], an
extension to other areas should include separate validation and calibration to
ensure it performs appropriately in those settings. Alternatively, other wind
field modeling software is available that provides a global coverage, like
Geoscience Australia's Tropical Cyclone Risk Model
(http://geoscienceaustralia.github.io/tcrm/). Finally, the relevant geopolitical
boundaries to use for aggregation would vary by country (e.g., municipalities in
Mexico, districts in India).**"

@@

\medskip

\begin{shaded}
\textbf{R1 Comment 6:}
This is not a comment on the paper, but the authors may also want to consider
publishing their work in DesignSafe, which is "the web-based research platform
of the NHERI  [NSF-Funded Natural Hazards Engineering Research Infrastructure]
Network that provides the computational tools needed to manage, analyze, and
understand critical data for natural hazards research." It is the data
repository widely used by interdisciplinary hazards and disaster researchers.
\end{shaded}

**Response:**

This is a very good, and very forward-looking suggestion. And it turns out that
the data we present should already be accessible to use on the DesignSafe
platform because we have shared the data as an R package.

DesignSafe is an online platform sponsored by the National Science Foundation as
part of the Natural Hazards Engineering Research Infrastructure
[@rathje2017designsafe]. This platform can be used to store, share, and publish
citable data related to natural hazards through its Data Depot. It goes beyond a
data repository, however, and also allows researchers to conduct data
integration and analysis in the cloud through its Discovery Workspace, while
drawing on data stored in the Data Depot and while using scientific programming
tools. As part of its platform, DesignSafe allows users to work in a number of
programming languages, including R (through Jupyter Notebooks)
[@rathje2017designsafe]. Therefore, and thanks to the R package mechanism and
its integration into the R environment, DesignSafe users already have access to
any data shared through an R package.

This is a very useful feature because it might otherwise be difficult to try to
maintain copies of the dataset in different repositories (i.e., one copy as an R
package and another as a DesignSafe dataset), and there could be confusion about
the equivalence of the two copies. R packages are citable through a standard
format that gives the R package version, while data publicly shared on
DesignSafe is assigned a digital object identifiers (DOI)
[@rathje2017designsafe], and so different citations would be used for the same
dataset depending on how the user accessed it. If updates of one copy were not
immediately updated for the other copy, the copies could get out of sync, and
maintaining two synced copies would add would add an extra layer of work with
each update to the R package (we have been updating several hazards as new data
becomes available). DesignSafe’s interface with R avoids this problem by
allowing its users direct access to our package and its data through that path,
as it allows for a single, citable, licensed version of the data stored and
shared from a single location, with no question of syncing separate versions of
the data or clarifying licensing and citation practices across two storage
locations.

We have added a note in the manuscript to let readers know that, because the
data is shared through an R package, and because DesignSafe’s Discovery
Workspace allows users to work in R, the data can be fully accessed and used for
those working on the DesignSafe platform by using the same code in a DesignSafe
Jupyter notebook that would otherwise be used on a local computer.

@@

\input{tables/precip_high_corr.tex}

In several cases, the correlation was much weaker when limiting analysis to
these severe rainfall events. For example, in Miami-Dade County, FL, the
Spearman correlation coefficient was 0.94 for all 64 tropical cyclones that came
near the county over the analysis period, while it was only 0.49 among the 18
storms with cumulative precipitation of 75 mm or more. There was a similar
reduction in Mobile County, AL. However, for some counties, the correlation
remained high (e.g., Harris County, TX; Orleans Parish, LA), although in all
cases there are few extreme precipitation events (5--20 across
these sample counties), and so there is likely substantial random variation in
these correlation estimates, since they are based on small numbers of 
observations.

We have added text to mention this point and to direct readers to the added
supplemental table:

> **Text in revised Results (relevant addition in bold):**
"The rainfall data are generally well-correlated with ground-based
observations, but may sometimes underestimate very high rainfall values (Figure
2). **Further, in some counties, the correlation was substantially lower when 
considering only tropical cyclones with cumulative local rainfall of $\ge75$ mm
(Table S2)**."

> **Text in revised Discussion (relevant addition in bold):**
"The rainfall data are generally well-correlated with ground-based observations,
but may sometimes underestimate very high rainfall values (Figure 2), **and in
some counties the correlation was substantially lower when considering only
tropical cyclones with cumulative local rainfall of $\ge75$ mm (Table S2).**"

### 2020-09-22 ehp_revision/writing/ehp_discussion.tex
Finalize revisions for submission

\textbf{This dataset is limited to the contiguous US, and while expansion to
global coverage would be useful and feasible, there would be some challenges.
For precipitation data, the re-analysis product used here (NLDAS-2) only covers
the contiguous US, although other re-analysis products, as well as other types
of precipitation datasets, have global coverage \parencite{sun2018review}. The
wind data are generated based on a model that is currently US-focused
\parencite{stormwindmodel}, but could be extended to other areas, although this
would require adding new land/sea masks within the associated software, as well
as accounting for differences across storm basins in wind averaging periods
\parencite{harper2010guidelines} and in the direction of cyclonic winds in the
Northern versus Southern Hemisphere. Further, since the core of the wind model
was developed based on data from Atlantic-basin storms
\parencite{willoughby2006parametric}, an extension to other areas should
include separate validation and calibration to ensure it performs appropriately
in those settings. Alternatively, other wind field modeling software is
available that provides a global coverage, like Geoscience Australia's Tropical
Cyclone Risk Model (http://geoscienceaustralia.github.io/tcrm/). For tornado
and flood events, the data described in this paper drew on a US-focused storm
events database, and so international extension of data on these hazards would
require access to similar databases covering other countries. Finally, the
relevant geopolitical boundaries to use for aggregation would vary by country
(e.g., municipalities in Mexico, districts in India).}

@@

Second, these data are aggregated to the county level. \textbf{This spatial
scale allows for easy integration with health outcome data aggregated at the
county level. Such data is often used for disaster epidemiology, as aggregated
data may be easier to access than individual-level data, especially at a scale
that covers many locations and years and so allows higher statistical power and
includes a broader range of exposure levels
\parencite{wakefield2008overcoming}.}

>>>>

\textbf{This dataset is limited to the contiguous US, and while expansion to
global coverage would be useful and feasible, there would be some challenges.
The key challenge would be for tornado and flood events. For these events, the
data described in this paper drew on a US-focused storm events database, and so
international extension of data on these hazards would require access to
similar databases covering other countries.  For precipitation data, while the
re-analysis product used here (NLDAS-2) only covers the contiguous US, other
re-analysis products, as well as other types of precipitation datasets, have
global coverage \parencite{sun2018review}. The wind data are generated based on
a model that is currently US-focused \parencite{stormwindmodel}, but could be
extended to other areas, although this would require adding new land/sea masks
within the associated software, as well as accounting for differences across
storm basins in wind averaging periods \parencite{harper2010guidelines}.
Further, since the core of the wind model was developed based on data from
Atlantic-basin storms \parencite{willoughby2006parametric}, an extension to
other areas should include separate validation and calibration to ensure it
performs appropriately in those settings. Alternatively, other wind field
modeling software is available that provides a global coverage, like Geoscience
Australia's Tropical Cyclone Risk Model
(http://geoscienceaustralia.github.io/tcrm/). For tornado and flood events, the
data described in this paper drew on a US-focused storm events database, and so
international extension of data on these hazards would require access to
similar databases covering other countries. Finally, the relevant geopolitical
boundaries to use for aggregation would vary by country (e.g., municipalities
in Mexico, districts in India).}

@@

Second, these data are aggregated to the county level. \textbf{This spatial
scale allows for easy integration with health outcome data aggregated at the
county level, and disaster response decisions are often made at a county or
state level. Such data is often used for disaster epidemiology, as aggregated
data may be easier to access than individual-level data, especially at a scale
that covers many locations and years and so allows higher statistical power and
includes a broader range of exposure levels
\parencite{wakefield2008overcoming}.}
